---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, fig.retina = 2, message = FALSE, warning = FALSE
)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/madhttr.svg?branch=master)](https://travis-ci.org/hrbrmstr/madhttr) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/madhttr/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/madhttr)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/madhttr)](https://cran.r-project.org/package=madhttr)

# madhttr

Tidy Helper Methods for Many Types of Unkempt Internet Metadata and Content

## Description

The 'httr', 'openssl', and 'HARtools' packages provide methods to retrieve
rich metadata and content from internet hosts but their return objects are quite
unkempt. Methods are provided to turn these objects into tidy data frames along with
other useful helper methods which augment functionality in these packages.

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo = FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(madhttr)
library(tibble) # for printing

# current version
packageVersion("madhttr")

```

### Certifiable

```{r certs}
tidy_cert(download_ssl_cert("r-project.org"))
```

### Responsive

```{r resp}
tidy_response(GET("https://rud.is/b"))
```

### HARdy

```{r hardy}
tidy_har(readRDS(system.file("extdat", "example-har.rds", package = "madhttr")))
```

## madhttr Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
